Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-11-07 draft.tex
restate prop 1; change format of props to match defns

\newtheorem{definition}{Definition}
\newcommand{\ta}{\theta}
\newcommand{\Ta}{\Theta}
\newcommand{\ga}{\gamma}
\newcommand{\un}{\underline}
\newcommand{\ov}{\overline}
\newcommand{\de}{\delta}
\newcommand{\ve}{\varepsilon}
\linespread{1.05} % Palatino needs more leading (space between lines)
\title{Unrecognized States: A Theory of Self-Determination and Foreign Influence}

@@

\begin{quotation}
\noindent \bf \emph{Proposition 1:} \rm  \emph{There exists an equilibrium in which the outcome is perpetual unrecognized statehood. The actions in this equilibrium are for $p$ to invest to create a buffer of $\frac{\beta}{1-\de}$ between the payoffs from ceding and the status quo in the first period and to invest up to $\mu$ each period thereafter to maintain the buffer; for $c$ to pay nothing; and for both $g$ and $s$ to play $Status$ $Quo$ each period.}

\end{quotation}

@@

\begin{quotation}
\noindent \bf \emph{Proposition 2:} \rm  \emph{Assume the conditions of \emph{Proposition 1} hold in the absence of sanctions and that sanctions affect only player $s$'s payoffs to maintaining the Status Quo. In order for sanctions to lead to ceding by the secessionists, the following are required:}

@@

\item \textit{The secessionists' continuation value from playing Cede must be higher than their continuation value from playing Fight. }
\end{enumerate}

\end{quotation}

@@

\begin{quotation}
\noindent \bf \emph{Proposition 3:} \rm  \emph{Assume the conditions of \emph{Proposition 1} hold in the absence of sanctions and that sanctions affect both player $s$'s status quo payoffs and its military capabilities. The parameter space over which a war will be initiated by the home state is increasing in the magnitude of the sanctions' impact on the secessionists' military capabilities.}

\end{quotation}

>>>>

\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}
\newcommand{\ta}{\theta}
\newcommand{\Ta}{\Theta}
\newcommand{\ga}{\gamma}
\newcommand{\un}{\underline}
\newcommand{\ov}{\overline}
\newcommand{\de}{\delta}
\newcommand{\ve}{\varepsilon}
\linespread{1.05} % Palatino needs more leading (space between lines)
\title{Unrecognized States: A Theory of Self-Determination and Foreign Influence}

@@

\begin{proposition}
	For any game in the class of games $\mathcal{G}$, there exists at least one Status Quo Equilibrium.
\end{proposition}

@@

\begin{proposition}
Assume the conditions of \emph{Proposition 1} hold in the absence of sanctions and that sanctions affect only player $s$'s payoffs to maintaining the Status Quo. In order for sanctions to lead to ceding by the secessionists, the following are required:

@@

\item \textit{The secessionists' continuation value from playing Cede must be higher than their continuation value from playing Fight.}
\end{enumerate}

\end{proposition}

@@

\begin{proposition}
Assume the conditions of \emph{Proposition 1} hold in the absence of sanctions and that sanctions affect both player $s$'s status quo payoffs and its military capabilities. The parameter space over which a war will be initiated by the home state is increasing in the magnitude of the sanctions' impact on the secessionists' military capabilities.

\end{proposition}
